A Bayesian Approach to Knowledge Graph Node Embeddings

### 2017-08-12 kgpsr/kgpsr.tex
...

\title{A Variational Approach to Knowledge Graph Node Embeddings}

@@

	We present a Variational approach to to the problem of embedding knowledge graph nodes.
\end{abstract}

\section{Introduction}
Knowledge graph node embeddings are vector representations of the nodes in a knowledge graph. For a knowledge graph with nodes $N$, an embedding is a function $v: N \to \R^k$ such that $v$ organizes the nodes meaningfully in the spacer $\R^k$ according to some criterion.

Effective embeddings are an important first step in many pipelines for knowledge graph visualisation, completion, classification and other tasks. Many embedding algorithms model the relations in the knowledge graph as maps in the embedding space: either translations, or more complex transformations. If for instance, we have the triple $(\fw{Mary}, \fw{childof}, \fw{John})$, then we learn embeddings $v_\fw{Mary}, v_\fw{John} \in \R^k$  (for some chosen embedding dimension $k$) and a map $f_\fw{childof} : \R^k \to \R^k$ for the relation \texttt{childof} such that $f_\fw{childof}(v_\fw{John})$ should be as close to $v_\fw{Mary}$ as possible (for some chosen distance metric).

@@

Intuitively, this is a simple latent variable problem, that can be solved by an alternating optimization algorithm in the vein of expectation-maximization: given a choice for the node embeddings, we can find the optimal functions to represent the relations, and given a choice for the relation functions, we compute the optimal embeddings. Alternating these two optimizations is likely to converge to a good solution. To formalize this intuition in an elegant manner, take a Bayesian approach, and find the optimum using variational inference. Thge preicsae model is detailed in Section~\ref{section:model}.

Our approach has several advantages over the alternatives:
\begin{itemize}
	\item The nodes are embedded in a simple Euclidean space, making no special demands on downstream architectures.
	\item The multiple-relation issue is solved in an intuitive manner: mapping a parent node to its children creates a probability distribution that covers the children. 
	\item The method is agnostic to the family of maps used to represent relations. We choose affine maps as a good tradeoff between ease of optimization, rigidity to protect against overfitting, and expressiveness. The method easily generalizes to other function classes.
	\item For linear maps, we can decompose the loss function into factors which can be solved analytically. Thus, the problem can be solved using an iterative algorithm which is guaranteed to converge to a local optimum.
	\item Negative sampling is not required. The basic framework constrains the problem sufficiently to lead to models that generalize well.
	\item The variational framework protects against convergence to solutions with singularities, and allows us to incorporate hyperparameters like the dimension of the embedding space into the optimization process.
\end{itemize}

@@

Let $x_i \in \R^k$ be the embedding chosen for node $i \in V$. Let $f_r$ be a parametrized function from $\cal F$, representing relation $r \in R$. For our method, we will let $\cal F$ be the set of affine functions, each parametrized by a transformation matrix $A_r \in \R^{k\times k}$, and a translation vector $t_r\in \R^k$. Thus our model contains $|N|$ vectors in $\R^k$, and $|R|$ functions each defined by a matrix $A_r$ and vector $t_r$.

@@

% TODO Read up on Bayes and conjugate priors. GEt a better sense of what priors I should use.

@@

>>>>

\title{A Bayesian Approach to Knowledge Graph Node Embeddings}

@@

	We present a variational approach to to the problem of embedding knowledge graph nodes.
\end{abstract}

\section{Introduction}
Knowledge graph node embeddings are vector representations of the nodes in a knowledge graph. For a knowledge graph with nodeset $N$, an embedding is a function $v: N \to \R^k$ such that $v$ organizes the nodes meaningfully in the space $\R^k$ according to some criterion.

Effective embeddings are an important first step in many pipelines for knowledge graph visualisation, completion, classification and other tasks. Many embedding algorithms model the relations in the knowledge graph as maps in the embedding space: either translations, or more complex transformations. If for instance, we have the triple $(\fw{Mary}, \fw{childof}, \fw{John})$, then we learn embeddings $v_\fw{Mary}, v_\fw{John} \in \R^k$  (for some chosen embedding dimension $k$) and a map $f_\fw{childof} : \R^k \to \R^k$ for the relation \texttt{childof} such that $f_\fw{childof}(v_\fw{John})$ should be as close to $v_\fw{Mary}$ as possible (for some chosen notion of distance).

@@

The task, then, given a knowledge graph, is to find an embedding $v_i$ for each node $i$, and a function $f_r$ for each relations, such that the resultant Gaussians optimally cover the required nodes. Intuitively, this problem can be solved by an alternating optimization algorithm in the vein of expectation-maximization: given a choice for the node embeddings, we can find the optimal functions to represent the relations, and given a choice for the relation functions, we can compute the optimal embeddings. Alternating these two optimizations is likely to converge to a good solution. To formalize this intuition in an elegant manner, we take a Bayesian approach, and find a solution using variational inference. The precise model is detailed in Section~\ref{section:model}.

Our approach has several advantages over the alternatives:
\begin{itemize}
	\item The nodes are embedded in a simple Euclidean space, making no special demands on downstream architectures. %TODO Check if ComplEx and HolE do actually do this. Explain better
	\item The multiple-relation issue is solved in an intuitive manner: mapping a parent node to its children creates a probability distribution that covers the children. 
	\item The method is agnostic to the family of maps used to represent relations. We choose affine maps as a good tradeoff between ease of optimization, rigidity to protect against overfitting, and expressiveness. The method easily generalizes to other function classes.
	\item For linear maps, we can decompose the loss function into factors which can be solved analytically. Thus, the problem can be solved using an iterative algorithm which is guaranteed to converge to a local optimum.
	\item Negative sampling is not required. The basic framework constrains the problem sufficiently to lead to models that generalize well.
	\item The variational framework protects against convergence to solutions with singularities, and allows us to incorporate hyperparameters like the dimension of the embedding space into the optimization process.
\end{itemize}

@@

Let $x_i \in \R^k$ be the embedding chosen for node $i \in V$. Let $f_r$ be a parametrized function from $\cal F$, representing relation $r \in R$. For our method, we will let $\cal F$ be the set of affine functions, each parametrized by a transformation matrix $A_r \in \R^{k\times k}$, and a translation vector $t_r\in \R^k$. Thus our model contains $|V|$ vectors in $\R^k$, and $|R|$ functions each defined by a matrix $A_r$ and vector $t_r$.

@@

% TODO Read up on Bayes and conjugate priors. Get a better sense of what priors I should use.

@@

If we have $(s, p, o) \in G$, then we have:
\begin{align*}
p(X_o \mid F_p = f_p) = f_p(p(X_s))(X_o) \\
p(X_s \mid F_p = f_p) = f_p^{-1}(p(X_o))(X_s) 
\end{align*}

Where $X_s$ are random variables over $\R^k$ representing the embedding of $s$, and $F_p$ is a random variable over $\cal F$ representing the function chosen for relation $p$. What this states, is that for a given choice of function embedding $f_p$, the probability distribution over $X_o$ can be found by taking the probability distribution over $X_s$, and transforming it by $f_p$. Starting with the joint distribution, and marginalizing out $F_p$:

\begin{align*}
p(X_o) = \int p(F_p = f_p) f_p(p(X_s))(X_o) df_p\\
p(X_s) = \int p(F_p = f_p) f_p(p(X_o))(X_s) df_p\\
\end{align*}

Which is a recursive, cyclic definition. Use KL divergence instead, to measure error.
